Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | AI & digital&nbsp;humanities&nbsp;instructor </font>

### 2023-09-21 index.Rmd
tartu

- Talk "Programming, data visualization & AI  for academic audiences across institutions and disciplines: lessons learned", at the Cross-university collaboration in Digital Humanities & Social Science (DHSS) and Digital Humanities & Cultural Heritage (DHCH) Education workshop of the DHNB2023 conference | [slides](https://datafigure.eu/reports/AndresKarjusDatafigure_CrossUniversityDHworkshop.pdf)
- Talk "Exploring Estonian Public Television Production 2004-2020 Using Big Programming Data" at the 8th Estonian Digital Humanities [Conference](https://dh.org.ee/events/dhe2022) (05.10.2022)
- Poster "Evolving Linguistic Divergence in Socio-Political Polarities", at the [JCoLe](https://sites.google.com/view/joint-conf-language-evolution) Joint Conference on Language Evolution in Kanazawa, Japan (August 2022)
- Poster "Linguistic divergence in American English along socio-political polarities", the [IC2S2](https://www.ic2s2.org/) Computational Social Science Conference (20.07.2022) | [pdf](https://andreskarjus.github.io/talks/ic2s2/IC2S2_poster_Linguistic_divergence_in_American_English_along_socio-political_polarities.pdf)
- Seminar talk at the Poncelet laboratory in Moscow (November 2021)
- [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) (October 2021) | [slides](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)
- [Protolang 7](https://blogs.phil.hhu.de/protolang7/programme/) (September 2021) | [slides](https://andreskarjus.github.io/talks/andres_karjus_protolang7.pdf)
- [Culture Conference 2021](https://culture-conference.com/) | [Poster on aesthetic complexity](https://andreskarjus.github.io/talks/cultureconference2021/)
- [TÜling](https://www.keel.ut.ee/et/tuling) (April 2021)
- [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

>>>>

- Talk on LLMs for studying texts and change at "Assessing and measuring systems change" workshop | [slides](https://andreskarjus.github.io/talks/Tartu_LLMtalk.pdf)
- Poster on film festival research at Netsci 2023, Vienna
- Presentation at the Bibliotheca Herziana workshop on computational approaches to art
- Talk "Programming, data visualization & AI  for academic audiences across institutions and disciplines: lessons learned", at the Cross-university collaboration in Digital Humanities & Social Science (DHSS) and Digital Humanities & Cultural Heritage (DHCH) Education workshop of the DHNB2023 conference | [slides](https://datafigure.eu/reports/AndresKarjusDatafigure_CrossUniversityDHworkshop.pdf)
- Talk "Exploring Estonian Public Television Production 2004-2020 Using Big Programming Data" at the 8th Estonian Digital Humanities [Conference](https://dh.org.ee/events/dhe2022) (05.10.2022)
- Poster "Evolving Linguistic Divergence in Socio-Political Polarities", at the [JCoLe](https://sites.google.com/view/joint-conf-language-evolution) Joint Conference on Language Evolution in Kanazawa, Japan (August 2022)
- Poster "Linguistic divergence in American English along socio-political polarities", the [IC2S2](https://www.ic2s2.org/) Computational Social Science Conference (20.07.2022) | [pdf](https://andreskarjus.github.io/talks/ic2s2/IC2S2_poster_Linguistic_divergence_in_American_English_along_socio-political_polarities.pdf)
- Seminar talk at the Poncelet laboratory in Moscow (November 2021)
- [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) (October 2021) | [slides](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)
- [Protolang 7](https://blogs.phil.hhu.de/protolang7/programme/) (September 2021) | [slides](https://andreskarjus.github.io/talks/andres_karjus_protolang7.pdf)
- [Culture Conference 2021](https://culture-conference.com/) | [Poster on aesthetic complexity](https://andreskarjus.github.io/talks/cultureconference2021/)
- [TÜling](https://www.keel.ut.ee/et/tuling) (April 2021)
- [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_
